Using Occupancy Theory and Hierarchical Models to Estimate Otter Population in Southeastern Minnesota

### 2010-02-28 Paper.tex

    \subsection{False positive rates}
    The lack of consistency among the flights is strong evidence that the data
    contain false positives where scientists think they see a track when it does
    not exist. Not accounting for such a process can lead to major biases; as
    the number of flights increases, the occupancy rate estimate will approach
    1 \cite{Royle2006}. Unlike most occupancy models where scientists assume 
    that detection of the species in question guarantees its presence \cite
    {MacKenzie2006}, we introduced a false detection process whereby an observer 
    can mark down the existence of a track when in reality there is none. This 
    false detection process can occur as long as there is no track, whether or 
    not the site is occupied.

>>>>

    \subsection{False positive rates}
    The lack of consistency among the flights is strong evidence that the data
    contain false positives where observers think they see a track when it does
    not exist. Not accounting for such a process can lead to major biases; as
    the number of flights increases, the occupancy rate estimate will approach
    1 \cite{Royle2006}. Unlike most occupancy models where observers assume 
    that detection of the species in question guarantees its presence \cite
    {MacKenzie2006}, we introduced a false detection process whereby an observer 
    can mark down the existence of a track when in reality there is none. This 
    false detection process can occur as long as there is no track, whether or 
    not the site is occupied.
